Accessing the nucleon tensor structure in inclusive deep inelastic scattering

### 2016-07-28 1607 - JMC for g2/Paper/JMC_dis.tex
Added bib and bst files

The transversity distribution is notoriously difficult to access because it is
a chiral-odd function and needs to be combined with a spin-flip mechanism to
appear in a scattering process~\cite{Jaffe:1996zw}. Usually, this spin flip is provided by another
nonperturbative distribution or fragmentation function, implying that
transversity cannot be accessed in inclusive DIS,
but only in more complex processes such as semi-inclusive DIS or Drell-Yan~\cite{Ralston:1979ys,Jaffe:1991kp,Jaffe:1993xb,Collins:1993kk}.

@@

\bibliographystyle{myrevtex}
\bibliography{mybiblio}

>>>>

The transversity distribution is notoriously difficult to access because it is
a chiral-odd function and needs to be combined with a spin-flip mechanism to
appear in a scattering process~\cite{Jaffe:1996zw}. Usually, this spin flip is provided by another
nonperturbative distribution or fragmentation function, implying that
transversity cannot be accessed in inclusive DIS,
but only in more complex processes such as semi-inclusive DIS or Drell-Yan~\cite{Ralston:1979ys,Jaffe:1991kp,Jaffe:1993xb,Collins:1992kk}.

@@

\bibliographystyle{myrevtex}
\bibliography{jetbiblio}
